---
title: "Yelp Analysis"
author: "Ran Li"
date: "11/30/2021"
output: 
  html_document:
    toc: true
    toc_float: true
    df_print: paged
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)


```

## Introduction

**Motivating question: why is there no Wawa foods in my neighborhood?**

**Hypothesis: Neighborhood level characteristics influence locations of restaurants/grocery stores**

To explore this hypothesis we will use [Yelp's publicly available data ](https://www.yelp.com/dataset)of businesses in their database. We will use ZCTA level neighborhood characteristics which has been put together as a part of the BCHC COVID Inequities Project.

## Data

### Yelp

Below is a preview of the Yelp data. It name, ZCTA, coordinate and some boolean attributes: grocery, healthy grocery, food, fast food.

```{r}
## Load Dependencies
library(tidyr)
library(dplyr)
library(leaflet)
library(ggplot2)
library(plotly)
library(reactable)
load("../Data/Clean/analysis_bundle.rdata")


clean__tidy_yelp %>% slice(1:25) %>%  reactable()

```
